\chapter{Need for this Book}

I am writing this book because there seems to be a lack of a good manual for cycling in 
modern times.

There have been books written for the Dark Ages of cycling, but there are few
resources for the modern infrastructure that's being built. 

The definitive book is, of course, Effective Cycling by John Forrester. This
book is really fun to read. Also, the tome is comprehensive: it covers everything to bike repair, to riding techniques to XXX.

However, Effective Cycling has a few problems.

First of all, it's really huge which makes it too inaccessible to anyone other than the hardcore bike nerds.

Second, it's  written with a certain political agenda. Not that being political is bad--we all are. However, many people find John's politics off putting. For one thing, as a former racer, and anon-cycling commuter, he was writing to the small subset of cyclists who love racing and try to emulate bicycle racers. Not that there's anything wrong with that.

However, his agenda--to ride as fast as possible with as few stops as possible--has thwarted the attempts of other cycling advocates to create infrastructure to make cycling comfortable, fun, and safe for ordinary people.

It's impossible to predict how much damage has done to US cycling due to the Effective Cycling movement, but it's likely that the United States had things been different.

Worse, Forrester's claims are both contrary to public opinion, contrary to common sense, and even contrary to the studies he claims to use to draw his conclusions on.

In fact, I was going to call this book More Effective Cycling until my princess and our lawyer suggested otherwise due to John's trademark on Effective Cycling. Thus, it has a much, much better name. Thanks John. And thanks for the dogged persistence on online forums which caused me to get more involved with both analyzing bicycle statistics and studies as well as writing this book. I love you John, and your disciple Serge.

I love all cyclists, and I think that there needs to be more love in the cycling world.

So, where's the cycling love?

It's right here in this book. 

% Sun Oct  9 08:26:39 PDT 2011
